Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-09 analysis/paper/paper.Rmd
added inline figure reference

The Deadwater Slough is an approximately 1.5 kilometer section of the mainstem Salmon River located roughly 5.8 river kilometers downstream from the town of North Fork, Idaho ***(publication quality map referenced here)***. The downstream end of the slough is located at the confluence of Dump Creek and the Salmon River. Around 1897, the failure of a small mining diversion reservoir in the Dump Creek drainage resulted in an erosion event that deposited substantial amounts of sediment at the confluence of the Salmon River, thereby creating an unnaturally slow and deep section in the river, spanning approximately 30 acres and averaging 68 m width. Both northern pikeminnow *Ptychocheilus oregonensis* and smallmouth bass *Micropterus dolomieu* inhabit the slough which likely provides favorable conditions for their feeding and growth (e.g., reduced water velocity, deep channel, warmer water temperature).

>>>>

The Deadwater Slough is an approximately 1.5 kilometer section of the mainstem Salmon River located roughly 5.8 river kilometers downstream from the town of North Fork, Idaho (Figure \@ref(fig:map)). The downstream end of the slough is located at the confluence of Dump Creek and the Salmon River. Around 1897, the failure of a small mining diversion reservoir in the Dump Creek drainage resulted in an erosion event that deposited substantial amounts of sediment at the confluence of the Salmon River, thereby creating an unnaturally slow and deep section in the river, spanning approximately 30 acres and averaging 68 m width. Both northern pikeminnow *Ptychocheilus oregonensis* and smallmouth bass *Micropterus dolomieu* inhabit the slough which likely provides favorable conditions for their feeding and growth (e.g., reduced water velocity, deep channel, warmer water temperature).
